---
title: "p8105_hw2_qilu2370"
author: "QiLu"
date: "9/28/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
```

## HW2

#Problem 1

First, I read data from datasets
```{r cars}
# read data and omit Mr. Trash sheet
sheet_data = read_excel("data/HealthyHarborWaterWheelTotals2018-7-28.xlsx", sheet = "Mr. Trash Wheel", range = "A2:N336")
sheet_data = janitor::clean_names(sheet_data)
sheet_data = na.omit(sheet_data, cols("dumpster"))
sheet_data$sports_balls = as.integer(round(sheet_data$sports_balls))
```


```{r}
# read 2018 and 2017 data
data_2018 = read_excel("data/HealthyHarborWaterWheelTotals2018-7-28.xlsx", sheet = "2018 Precipitation", range = "A2:B14") %>%
  mutate(year = "2018")

data_2018 = data_2018%>% drop_na(Total)

data_2017 = read_excel("data/HealthyHarborWaterWheelTotals2018-7-28.xlsx", sheet = "2017 Precipitation", range = "A2:B14") %>%
  mutate(year = "2017")

data_2017 = data_2017%>% drop_na(Total)

```


```{r}

#merge them
join_data = full_join(data_2018,data_2017, by = c("Month"))

names(join_data) = c("Month", "Total", "Year", "Total", "Year")
join_data$Month = month.name

```

For the analysis part,
the number of observation of dumpsters we saw in 2017 was
```{r}
count_data_2017 = filter(sheet_data, year == 2017)
length(count_data_2017$dumpster)
```
the number of observation of dumpsters we saw in 2018 was
```{r}
count_data_2018 = filter(sheet_data, year == 2018)
length(count_data_2018$dumpster)
```
The number of dumpsters' observation increased.
  
Also, we can know the total precipitation in 2018 was
```{r}
total_2018 = replace_na(data_2018$Total, 0)
sum(total_2018)
```
  
the median number of sports balls in a dumpster in 2017 was
```{r}
median_data_2017 = filter(sheet_data, year == 2017)
median(median_data_2017$sports_balls)
```

  
the median number of sports balls in a dumpster in 2018 was
```{r}
median_data_2018 = filter(sheet_data, year == 2018)
median(median_data_2018$sports_balls)
```
we saw a significantly decrease.
  
Finally, the total number of weights in 2017 was
```{r}
total_wei_2017 = filter(sheet_data, year == 2017)
sum(total_wei_2017$weight_tons)
```

the total number of weights in 2018 was
```{r}
total_wei_2018 = filter(sheet_data, year == 2018)
sum(total_wei_2018$weight_tons)
```
the total weight we observed increased from 2017 to 2018.

And the total volume cubic yard in 2017 is
```{r}
total_vol_2017 = filter(sheet_data, year == 2017)
sum(total_vol_2017$volume_cubic_yards)
```
the total volume cubic yard in 2018 is
```{r}
total_vol_2018 = filter(sheet_data, year == 2018)
sum(total_vol_2018$volume_cubic_yards)
```
an increase was observered on the total cubic yard as well as the total weight.
  
The average of the weight per dumpster carrying in 2017 was
```{r}
sum(total_wei_2017$weight_tons)/length(count_data_2017$dumpster)

```
  
The average of the weight per dumpster carrying in 2018 was
```{r}
sum(total_wei_2018$weight_tons)/length(count_data_2018$dumpster)

```
From the figures above, we can observe that some type of items that dumpsters caught was changed a little bit, but the total amount of items and the total volume increased. Also, the weight per dumpster carrying in 2018 is higher than that of 2017. 
  
  
#Problem 2

```{r}
pols_month = read_csv(file = "./data/pols-month.csv")
pols_month = separate(pols_month, mon, c ("year", "month", "day"))
# ??????pols_month$month = month.name(as.Date(pols_month$month))

  
```


## Including Plots



```{r pressure, echo=FALSE}
plot(pressure)
```

