---
title: "p8105_hw2_qilu2370"
author: "QiLu"
date: "9/28/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
```

## HW2

#Problem 1

First, I read data from datasets
```{r cars}
# read data and omit Mr. Trash sheet
sheet_data = read_excel("data/HealthyHarborWaterWheelTotals2018-7-28.xlsx", sheet = "Mr. Trash Wheel", range = "A2:N336")
sheet_data = janitor::clean_names(sheet_data)
sheet_data = na.omit(sheet_data, cols("dumpster"))
sheet_data$sports_balls = as.integer(round(sheet_data$sports_balls))
```


```{r}
# read 2018 and 2017 data
data_2018 = read_excel("data/HealthyHarborWaterWheelTotals2018-7-28.xlsx", sheet = "2018 Precipitation", range = "A2:B14") %>%
  mutate(year = "2018")

data_2018 = data_2018%>% drop_na(Total)

data_2017 = read_excel("data/HealthyHarborWaterWheelTotals2018-7-28.xlsx", sheet = "2017 Precipitation", range = "A2:B14") %>%
  mutate(year = "2017")

data_2017 = data_2017%>% drop_na(Total)

```


```{r}

#merge them
join_data = full_join(data_2018,data_2017, by = c("Month"))

names(join_data) = c("Month", "Total", "Year", "Total", "Year")
join_data$Month = month.name

```

For the analysis part,
the number of observation of dumpsters we saw in 2017 was
```{r}
count_data_2017 = filter(sheet_data, year == 2017)
length(count_data_2017$dumpster)
```
the number of observation of dumpsters we saw in 2018 was
```{r}
count_data_2018 = filter(sheet_data, year == 2018)
length(count_data_2018$dumpster)
```
The number of dumpsters' observation increased.
  
Also, we can know the total precipitation in 2018 was
```{r}
total_2018 = replace_na(data_2018$Total, 0)
sum(total_2018)
```
  
the median number of sports balls in a dumpster in 2017 was
```{r}
median_data_2017 = filter(sheet_data, year == 2017)
median(median_data_2017$sports_balls)
```

  
the median number of sports balls in a dumpster in 2018 was
```{r}
median_data_2018 = filter(sheet_data, year == 2018)
median(median_data_2018$sports_balls)
```
we saw a significantly decrease.
  
Finally, the total number of weights in 2017 was
```{r}
total_wei_2017 = filter(sheet_data, year == 2017)
sum(total_wei_2017$weight_tons)
```

the total number of weights in 2018 was
```{r}
total_wei_2018 = filter(sheet_data, year == 2018)
sum(total_wei_2018$weight_tons)
```
the total weight we observed increased from 2017 to 2018.

And the total volume cubic yard in 2017 is
```{r}
total_vol_2017 = filter(sheet_data, year == 2017)
sum(total_vol_2017$volume_cubic_yards)
```
the total volume cubic yard in 2018 is
```{r}
total_vol_2018 = filter(sheet_data, year == 2018)
sum(total_vol_2018$volume_cubic_yards)
```
an increase was observered on the total cubic yard as well as the total weight.
  
The average of the weight per dumpster carrying in 2017 was
```{r}
sum(total_wei_2017$weight_tons)/length(count_data_2017$dumpster)

```
  
The average of the weight per dumpster carrying in 2018 was
```{r}
sum(total_wei_2018$weight_tons)/length(count_data_2018$dumpster)

```
From the figures above, we can observe that some type of items that dumpsters caught was changed a little bit, but the total amount of items and the total volume increased. Also, the weight per dumpster carrying in 2018 is higher than that of 2017. 
  
  
#Problem 2

```{r}
pols_month = read_csv(file = "./data/pols-month.csv")


pols_month = separate(pols_month, mon, c ("year", "month", "day")) %>%
  mutate(
    month = as.numeric(month),
    month = month.abb[month] ) 

president <- pols_month [,1]
president <- president==1
president <- cumsum(president)

pols_month= mutate(pols_month, 
       president = replace(president, prez_gop == "1","gop"),
       president = replace(president, prez_gop == "2","gop"),
        president = replace(president, prez_dem == "1","dem"),
       president = replace(president, prez_dem == "2","dem"),) %>%
  select(-prez_dem) %>%
  select(-prez_gop) %>%
  select(-day)
  
```

For snp.csv

```{r}
snp_data = read_csv(file = "./data/snp.csv")
snp_data = separate(snp_data, date, c ("month", "day", "year")) %>%
  mutate(
    month = as.numeric(month),
    month = month.abb[month],)
  
snp_data<- snp_data[,c("year", "month", "close")]
```



```{r}
unemployment_data = read_csv(file = "./data/unemployment.csv")
unemployment = 
  pivot_longer(
    unemployment_data, 
    Jan:Dec,
    names_to = "month", 
    values_to = "unemployment") 
  

unemployment = unemployment[order(unemployment$Year, decreasing = FALSE),]
names(unemployment) = c("year", "month", "unemployment")

```

merge step
```{r}
snp_data = snp_data[order(snp_data$month, decreasing = FALSE),]
snp_data = snp_data[order(snp_data$year, decreasing = FALSE),]


join_data = right_join(pols_month, snp_data)

unemployment$year = as.character(unemployment$year)

join_data = right_join(join_data, unemployment, by = c("year", "month"))
```
  
In the above datasets, pols_month contains the number of national politicians who are democratic or republican at any given time; snp_data contanis Standard & Poor’s stock market index (S&P) at any given time; unempolyment contains percentages of unemployment in different months of the associated year. After merging snp into pols, the joint dataset is one more column that contains the close snp than the pols before. Then, merging unemployment into the result, which can provide the percentage of unemployment at given time. 
  
#Problem 3

```{r}
baby_name = read_csv(file = "./data/Popular_Baby_Names.csv")
baby_name = janitor::clean_names(baby_name)
baby_name$childs_first_name = tolower(baby_name$childs_first_name)

# Remove duplicate rows of the dataframe using cyl and vs variables
baby_name = distinct(baby_name, year_of_birth, gender, childs_first_nameethnicity, count, rank, .keep_all= TRUE)

baby_name$ethnicity[baby_name$ethnicity == "BLACK NON HISP"] <- "BLACK NON HISPANIC"
baby_name$ethnicity[baby_name$ethnicity == "WHITE NON HISP"] <- "WHITE NON HISPANIC"

# select olivia
olivia_data = filter(baby_name, childs_first_name == "olivia") %>%
  select(-gender, -childs_first_name, -count)


olivia_data = pivot_wider(
  olivia_data, 
  names_from = "year_of_birth", 
  values_from = "rank")

olivia_data
```

```{r}
male_name = filter(baby_name, gender == "MALE" , rank == "1") %>% 
  select(-gender, -count) 


male_name = pivot_wider(
  male_name,
  names_from = "year_of_birth",
  values_from = "rank"
)
male_name
```
  
  
Plot part

```{r}
plot_data = filter(baby_name, gender == "MALE", year_of_birth == "2016", ethnicity == "WHITE NON HISPANIC")

polt_df = ggplot(plot_data, aes(x= rank, y = count)) +
  geom_point(aes(color = childs_first_name, alpha = .5)) +
  geom_smooth(se = FALSE)

polt_df
```


